---
title: "ETC5512_Tutorial4"
date: 1 Apr 2026
format: html
---

# Task 1: Working with Figures

```{r}
```{r}
#| label: fig-penguins-scatter
#| fig-cap: "Body mass vs. Flipper length for three penguin species."
#| warning: false
library(ggplot2)
library(palmerpenguins)

ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point() +
  theme_minimal()
```

@fig-penguins-scatter illustrates the relationship between body mass and flipper length got different penguin species

# Task 2: Creating Professional Tables

```{r}
```{r}
#| label: tbl-penguin-summary
#| tbl-cap: "Mean body mass of penguins by species and sex."
library(dplyr)

penguins |>
  filter(!is.na(sex)) |>
  group_by(species, sex) |>
  summarise(mean_mass = mean(body_mass_g)) |>
  knitr::kable()
```

@tbl-penguin-summary summaries the body mass of penguins by species and sex.

# Task 3: Dynamic Cross-Referencing
As shown in @fig-penguins-scatter, there is a clear positive correlation between flipper length and body mass. This means when the flipper length increases, the penguins are heavier.

The specific average for each group are detailed in @tbl-penguin-summary. Gentoo penguin has the heaviest weight among others for both male and femail, while female Adelie has the lowest weight.